\documentclass[12pt]{article}
\input{header.tex}

\begin{document}

	\onehalfspacing
	In the process of writing this paper, progress has been slow and
	arduous. Numerous writer's blocks was encountered. The initial
	methodology was a random gathering of newspaper articles in an effort to
	support the topic, but I realized later on it was a foolish and futile
	exercise. It was no proper methodology and would lead me to nowhere.
	Later on, with the help of EG Dizon, we figured that it would be much
	better if I focused on a few publications leading me to look at China
	Daily and People's Daily. It was during these points where the
	methodology was vastly improved.

	The new methodology was naive, but worked. A simple search for the
	keyword ``starbucks'' in each of the respective sites and a little
	automation.  Basing from a project from previous semesters, I rewrote a
	small Python script which let me programatically download all the
	articles from China Daily and People's Daily that matched the keyword.
	Further discussions with EG resulted in the conclusion that it would be
	much better to focus on just one, and it would be People's Daily.
	Combing through China Daily's 800++ articles after sorting would be too
	tedious and unmanageable.

	Resulting news articles from People's Daily was then narrowed down to
	the last six and a half years (2010-01 to 2016-05) and then further
	sorted if it were in scope or otherwise. The resulting analysis was
	tallied into a spreadsheet. Although, this was already very protracted.

	Several times I've tried to work this through the night but in all
	honesty, I could start writing out of...fear? or anxiety? One of the
	biggest wastes of time I've had was attempting to cite a statement, I
	tried to search for the source and then ending up down a rabbit hole of
	straying out of path.

\end{document}

% vim: breakindent smartindent syntax=tex tw=80
